Radiocarbon measurement of CO~2~ from carbonate minerals using a gas ion source with an open split interface

### 2021-10-14 doc/AMS-15/AMS-15_poster.Rmd
Hide some plots

```{r}
ggplot(combined_results) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(fm_corr, fm_diff, color = method, shape = method,
                      ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr),
                  size = 1) +
  labs(title = "Haiti Core Graphite vs HGIS",
       x = "Fraction modern",
       y = "Fm - mean Fm")
```

No outliers

```{r}
combined_results %>% 
  filter(abs(fm_diff) < 0.02) %>% 
ggplot() +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(fm_corr, fm_diff, color = method, shape = method,
                      ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr),
                  size = 1) +
  labs(title = "Haiti Core Graphite vs HGIS",
       x = "Fraction modern",
       y = "Fm - mean Fm")
```

Highlight outliers

```{r}
ggplot(combined_results) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(fm_corr, fm_diff, color = method, shape = method,
                      ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr),
                  size = 1) +
  gghighlight(abs(fm_diff) > 0.02,
              #unhighlighted_params = list(colour = NULL),
              keep_scales = TRUE) +
  labs(title = "Haiti Core Graphite vs HGIS",
       x = "Fraction modern",
       y = "Fm - mean Fm")
```

All in one.

```{r}
outlier_df <- combined_results %>% 
  filter(abs(fm_diff) > 0.02)

>>>>

```{r, eval = FALSE}
ggplot(combined_results) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(fm_corr, fm_diff, color = method, shape = method,
                      ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr),
                  size = 1) +
  labs(title = "Haiti Core Graphite vs HGIS",
       x = "Fraction modern",
       y = "Fm - mean Fm")
```

```{r}
# No outliers
combined_results %>% 
  filter(abs(fm_diff) < 0.02) %>% 
ggplot() +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(depth, fm_diff, color = method, shape = method,
                      ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr),
                  position = "jitter") +
  labs(title = "Haiti Core Graphite vs HGIS",
       x = "Core depth (cm)",
       y = "Fm - mean Fm")
```

```{r, eval=FALSE}
# Highlight outliers
ggplot(combined_results) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(fm_corr, fm_diff, color = method, shape = method,
                      ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr),
                  size = 1) +
  gghighlight(abs(fm_diff) > 0.02,
              #unhighlighted_params = list(colour = NULL),
              keep_scales = TRUE) +
  labs(title = "Haiti Core Graphite vs HGIS",
       x = "Fraction modern",
       y = "Fm - mean Fm")
```

```{r eval=FALSE}
#All in one.

outlier_df <- combined_results %>% 
  filter(abs(fm_diff) > 0.02)
